Navigating to a greener Europe with 24/7 hourly carbon-free electricity procurement

### 2023-10-06 manuscript/sections/introduction.tex
intro: contribution and prologue

\textbf{The key problem --} When \gls{ci} consumers purchase renewable credits, either via unbundled schemes or via bundled \gls{ppa}s, renewable energy supply is typically matched over a long period of time with buyers' energy demands.
As an example, more than 400 members of the RE100 group\footnote{\url{https://www.there100.org/}} have committed to purchasing renewable energy that matches 100\% of their electricity consumption on an annual basis.
Even the \enquote{best case} of the 100\% annual matching commitments, where energy buyers sign \gls{ppa}s with renewable energy generators located within a local grid, has a major problem -- the temporal mismatch between renewable energy supply and electricity demand.
In hours when wind and solar generation is low, energy buyers have to depend on carbon-emitting technologies, like coal and gas, available on local markets.
As a result, the 100\% annual renewable matching approach does not entirely eliminate carbon emissions from the energy buyers portfolio.
Furthermore, 100\% annual matching approach keeps electricity buyers exposed to price volatility, as the price of electricity on the wholesale markets can vary significantly from hour to hour.

@@

Google broke the 24/7 ground in 2020 by announcing its commitment to entirely on the 24/7~CFE approach at all its data centres and campuses worldwide by 2030 \cite{google-247by2030}.
Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap}.
Also, Microsoft has committed to the 100/100/0 by 2030 goal (i.e. \enquote{100\% of electricity consumption, 100\% of the time, matched by zero carbon energy purchases} \cite{Microsoft-vision}. 
The list of entities that have committed to 24/7~CFE procurement includes also utilities, such as Peninsula Clean Energy (a community choice aggregator in California) committed to 24/7~CFE by 2025 \cite{peninsula-OurPathto247}, and even cities like Des Moines, Iowa U.S., with a commitment by 2035 \cite{iowaenvcouncil-247}. In 2021, an international group of energy suppliers, buyers, and \gls{ngo}s launched the 24/7 Carbon-free Energy Compact.\footnote{\url{https://gocarbonfree247.com/}}
With over 135 signatories, the group aims to \enquote{develop and scale high-impact technologies, energy policies, procurement practices, aand solutions to make 24/7 Carbon-Free Energy achievable for all}.

@@

\textbf{Existing literature on 24/7 CFE --} The growing interest in the means, costs and the system-level impacts of hourly \gls{cfe} procurement created a need for a quantitative analysis of the approach.
The existing model-based studies on 24/7~CFE approach are very recent.
The first to incorporate it into the electricity system planning model were Xu et al. (Oct 2022) \cite{xu-247CFE-SSRN}.\footnote{A working paper updates a prior public technical report (Nov 2021, \cite{xu-247CFE-report}) investigating the system-level impacts of 24/7~CFE in two regions of the U.S. -- California and PJM.} 
The authors study the system-level impacts of 24/7~CFE procurement based on an example of California in the year 2030.
In Nov 2022, IEA also released a model-based study on the 24/7~CFE, focusing on India and Indonesia \cite{ieaAdvancingDecarbonisationClean2022}.
In early 2023, Peninsula Clean Energy published an own white paper introducing their modeling tool---MATCH (Matching Around-the-Clock Hourly energy)---and the results of the modeling indicating feasibility of the company's \enquote{24/7 renewable energy by 2025} goal \cite{peninsula-report247}.

The first studies indicate that 24/7 CFE matching results in emission reduction for both energy buyers and the entire energy system, and has a potential to create demand pull for new clean energy technologies.
What has been missing is a comprehensive analysis of 24/7 procurement over multiple regions and years, since electricity system characteristics, National Climate and Energy Plans (\gls{necp}s), renewable resource quality, and the cost of clean energy vary significantly across regions and over time.
Furthermore, it is unclear whether decarbonisation effect of 24/7 CFE procurement remains relevant when electricity grids are progressively decarbonised, as is the case in many countries and jurisdictions, or if the 24/7~CFE procurement is only impactful in the early stages of the energy transition.

@@

% would be good to generalize 
as provided in this paper.

In this study, we model 24/7~CFE procurement in Europe up to 2030. 
We explore different designs, costs, benefits and impacts of the 24/7 approach, both for Google and for the power systems in which the data centres are located. 
In sum, we want to find out:

\begin{enumerate}
    \item How can we achieve hourly clean energy matching? 
    \item What is the 24/7~CFE cost premium versus the 100\% annual matching with renewables? 
    \item To which extent can technologies, such as long-duration storage or new dispatchable clean technologies, help to achieve the 24/7~CFE goal? 
    \item If many companies follow the 24/7~CFE approach, how does this effect the rest of the energy system?
\end{enumerate}

@@

>>>>

\textbf{The key problem --} When \gls{ci} consumers purchase renewable credits, either via unbundled schemes or via bundled \gls{ppa}s, renewable energy supply is typically matched over a long period of time with buyers' energy demands.
As an example, more than 400 members of the RE100 group \cite{re100report-2020} have committed to purchasing renewable energy that matches 100\% of their electricity consumption on an annual basis.
Even the \enquote{best case} of the 100\% annual matching commitments, where energy buyers sign \gls{ppa}s with renewable energy generators located within a local grid, has a major problem -- the temporal mismatch between renewable energy supply and electricity demand.
In hours when wind and solar generation is low, energy buyers have to depend on carbon-emitting technologies, like coal and gas, available on local markets.
As a result, the 100\% annual renewable matching approach does not entirely eliminate carbon emissions from the energy buyers portfolio.
Furthermore, 100\% annual matching approach keeps electricity buyers exposed to price volatility, as the price of electricity on the wholesale markets can vary significantly from hour to hour.

@@

Google broke the 24/7 ground in 2020 by announcing its commitment to entirely on the 24/7~CFE approach at all its data centres and campuses worldwide by 2030 \cite{google-247by2030}.
Shortly after, Google published a policy roadmap on achieving the goal \cite{google-PolicyRoadmap}.
Also, Microsoft has committed to the 100/100/0 by 2030 goal (i.e. \enquote{100\% of electricity consumption, 100\% of the time, matched by zero carbon energy purchases} \cite{Microsoft-vision}. 
The list of entities that have committed to 24/7~CFE procurement includes also utilities, such as Peninsula Clean Energy (a community choice aggregator in California) committed to 24/7~CFE by 2025 \cite{peninsula-OurPathto247}, and even cities like Des Moines, Iowa U.S., with a commitment by 2035 \cite{iowaenvcouncil-247}. In 2021, an international group of energy suppliers, buyers, and \gls{ngo}s launched the 24/7 Carbon-free Energy Compact \cite{gocarbonfree247}.
With over 135 signatories, the group aims to \enquote{develop and scale high-impact technologies, energy policies, procurement practices, aand solutions to make 24/7 Carbon-Free Energy achievable for all}.

@@

\textbf{Existing literature on 24/7 CFE --} The growing interest in the means, costs and the system-level impacts of hourly \gls{cfe} procurement created a need for a quantitative analysis of the approach.
The existing model-based studies on 24/7~CFE approach are very recent.
The first to incorporate it into the electricity system planning model were Xu et al. (2022) \cite{xu-247CFE-SSRN}.\footnote{A working paper updates a prior public technical report published in November 2021 investigating the system-level impacts of 24/7~CFE in two regions of the U.S. -- California and PJM \cite{xu-247CFE-report}.} 
The authors study the system-level impacts of 24/7~CFE procurement based on an example of California in the year 2030.
In November 2022, IEA also released a model-based study on the 24/7~CFE, focusing on India and Indonesia \cite{ieaAdvancingDecarbonisationClean2022}.
In early 2023, Peninsula Clean Energy published an own white paper introducing their modeling tool---MATCH (Matching Around-the-Clock Hourly energy)---and the results of the modeling indicating feasibility of the company's \enquote{24/7 renewable energy by 2025} goal \cite{peninsula-report247}.

The first studies indicate that voluntary 24/7~CFE commitments reduce the emissions of participating buyers as well as emissions in the electricity grids they operate.
What has been missing is a comprehensive analysis of 24/7~CFE procurement over multiple regions and years, since electricity system characteristics, National Climate and Energy Plans (\gls{necp}s), renewable resource quality, and the cost of clean energy vary significantly across regions and over time.
Furthermore, it is unclear whether decarbonisation effect of 24/7 CFE procurement remains relevant when electricity grids are progressively decarbonised, as is the case in many countries and jurisdictions, or if the 24/7~CFE procurement is only impactful in the early stages of the energy transition.

@@

\textbf{Contribution --} The goal of this work is to systematically explore different designs, optimal procurement strategies, costs, benefits and impacts of the 24/7~CFE matching approach, both for participating buyers and for regions where voluntary procurement occurs.
Our analysis focuses on four regions within the European energy system with unique characteristics, and we vary the analysis years to track the evolution of the energy system.
Additionally, we examine the underlying mechanisms that drive the system-level reduction of \co emissions, and examine how they perform over time and across regions.

@@

The remainder of the paper is structured as follows: Section \cref{sec:methods} gives a brief summary of methodology, sources of model input data, and the experimental setup. The results are presented and discussed in Section \cref{sec:results} and put in perspective in Section \cref{sec:discussion}. The work is concluded in Section \cref{sec:conclusion}.
